### 2015-04-29 analysis/e5_analysis_BP.Rmd
Analysis with ben tweaks

```{r}
rm(list=ls())
source("analysis/useful_dplyr.R")
library("rjson")
```

@@

```{r}
files <- dir("production-results/e5/", pattern = "*.json")
d.raw <- data.frame()

for (f in files) {
  jf <- paste("production-results/e5/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- data.frame(workerid = jd$WorkerId, 
                   scale = jd$answer$scale,
                   degree = jd$answer$degree,
                   stars = jd$answer$manipulation_level,
                   judgment = as.numeric(jd$answer$judgment),
                   language = jd$answer$language)
  d.raw <- bind_rows(d.raw, id)
}
```

@@

pdf("plots/e5.pdf", width=8, height = 5)
qplot(x = stars, y = judgment, col = degree,
      geom = "line", stat = "identity", 
      position = "dodge", 
      data = ms) + 
  geom_linerange(aes(ymin = judgment - cil, 
                     ymax = judgment + cih)) + 
  facet_wrap(~scale)
dev.off()
```

>>>>

```{r}
rm(list=ls())
p = file.path("~/Desktop/Projects/scalar_implicature/")
source(paste0(p,"analysis/useful_dplyr.R"))
library("rjson")
```

@@

```{r}
files <- dir(paste0(p,"production-results/e5/"), pattern = "*.json")
d.raw <- data.frame()
f = "3X3OR7WPZZ0BL54CDY6ARQ6UXHB8L1.json"
for (f in files) {
  jf <- paste(p,"production-results/e5/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- data.frame(workerid = jd$WorkerId, 
                   scale = jd$answer$scale,
                   degree = jd$answer$degree,
                   stars = jd$answer$manipulation_level,
                   judgment = as.numeric(jd$answer$judgment),
                   language = jd$answer$language)
  d.raw <- bind_rows(d.raw, id)
}
```

@@

pdf(paste0(p,"plots/e5.pdf"), width=8, height = 5)
qplot(x = stars, y = judgment, col = degree,
      geom = "line", stat = "identity", 
      position = "dodge", 
      data = ms) + 
  geom_linerange(aes(ymin = judgment - cil, 
                     ymax = judgment + cih)) + 
  facet_wrap(~scale)
dev.off()
```
